PUT YOUR TITLE HERE

### 2023-03-17 paper/manuscript.Rmd
throw in some cites

---
title: PUT YOUR TITLE HERE
author:
  - name: Veronica Boyce
    affiliation: Stanford
    footnote:
      - corresp
  - name: Maya Mathur
    affiliation: Stanford
  - name: Michael C. Frank
    affiliation: Stanford
address:
  - code: Stanford
    address: Stanford University
footnote:
  - code: corresp
    text: "Corresponding author. Email: vboyce@stanford.edu"
bibliography: ["mybibfile.bib"] # Replace with one or more of your own bibtex files. Better BibTeX for Zotero is your friend
csl: dmk-format.csl # Use any CSL style. See https://www.zotero.org/styles for a good list. Ignored if citation_package: natbib
link-citations: TRUE
output:
  bookdown::pdf_document2:
    toc: FALSE
    keep_tex: TRUE
    template: generic_article_template.tex
    #md_extensions: "-autolink_bare_uris"
    number_sections: TRUE
    citation_package: default # Can also be "natbib"
lang: en # Main document language in BCP47 format
geometry: "margin=25mm"
papersize: a4
#linestretch: 2 # for double spacing
endfloat: FALSE # Set to TRUE to turn on latex endfloat package to place figures and tables at end of document
# endfloatoption: # See endfloat documentation for more possibilities
#   - tablesfirst # Default
#   - nomarkers # Default
numberlines: FALSE
authblk: TRUE # FALSE = author affiliations in footnotes; TRUE = author affiliations in a block below author names
footnotehyper: FALSE # TRUE will give you enhanced table footnote capabilities. Set to FALSE to be able to use French blocks. Needed due to what appears to be a latex bug.
urlcolor: blue
linkcolor: blue
citecolor: blue
graphics: TRUE # Needed to be able to include images
tables: TRUE # Needed to be able to include tables
# fancyhdr:
#   first:
#     #headleft: "REPORT-NO-XXXX"
#     headright: "Kaplan et al. (2021)"
#     headrulewidth: 0pt
#     #footleft: A left foot
#     footrulewidth: 0pt
#   subsequent:
#     #headleft: "NEXT-PAGE-HEADER-LEFT"
#     headright: "Kaplan et al. (2021)"
#     headrulewidth: 1pt
#     footrulewidth: 0pt

@@

We are aware of three large-scale replication efforts replicating experimental results in the existing psychology literature. The first is RP:P, which sampled roughly 100 studies from top psychology journals in 2008. They found an overall replication rate around 40%, which provided evidence to support growing concerns about the non-reliability of the literature. [idk, maybe worth framing that this was a big deal study when it came out]. TODO some discussion of how many papers have reanalysed this cutting the data different ways.

The ManyLabs series of studies have also done large-scale replications of effects from psychology. Due to their primary goal of investigating different forms of hetereogeneity, their sampling has been non-representive, focusing on short studies with only two conditions. Across Many labs 1-3 foo bar replicated. Many labs 5 was a re-replication attempt on 10 of RP:P and rescued 2/10. TODO look up details

Camerer replicated the 21 behaviors studies published in Nature and Science from 2010-2015 that did not require special populations or special equipment. They found a roughly 60% replication rate.

In addition to determining estimated overall replicaiton rates for fields and journals, there's also merit in knowing what features of experiments (and replication attempts) are predictive of replication success. Blah blah stakeholders and resources. There's some signal here, as people are able to predict replication success at above chance CITATIONS. RP:P looked at how replication rates varied across subsamples of their studies. They found that cognitive psychology studies replicated at higher, but still low rates (50% v 25%) compared to social psychology. They also found that larger effect sizes and smaller p-values of original studies were predictive of replicating. TODO do we talk about any other correlates. There are reasons to believe that experimental factors such as number of items or between and within subject designs may also be predictive (cite our old paper), and could pontentially be some of the reason for subfield differences.

[could possibly frame with a bit of some=MCF have advocated teaching replication cite whatever, describe class, then thing? ]
Here we introduce a new dataset of replications in the behavioral sciences, primarily psychology. Over the years 2011-2022, students in a graduate-level experimental methods class have conducted online replications as individual course projects. From this, we have 176 experimental replications that were codeable. This approximately doubles the set of experiments in the large-scale replication literature. We investigate predictors of replicability in this new dataset.

@@

@@

TODO write me! see Figure 2

@@

[ there is controversy here, but to even discuss it, we need empirics] Even those who argue that replication is not so essential still rely on data from replications to make their cases that replication rates are not as low as they seem and that these replication rates are acceptable.

@@

This subjective replication outcome was chosen because it already existed, could be applied to all projects (regardless of type and detail of statistical reporting), and did not rely solely on one statistical measure. As a complement, we also identified a "key" statistical test for each paper (see below for details), and if possible, computed p_original and prediction interval at this statistic (following CITE RPCB). p_original was a continuous measure of the p-value on the hypothesis that the original and replication samples come from the same distribution. Prediction interval was a binary measure of whether the replication outcome fell within the prediction interval of the original outcome measure.

>>>>

---
title: PUT YOUR TITLE HERE
author:
  - name: Veronica Boyce
    affiliation: Stanford
    footnote:
      - corresp
  - name: Maya Mathur
    affiliation: Stanford
  - name: Michael C. Frank
    affiliation: Stanford
address:
  - code: Stanford
    address: Stanford University
footnote:
  - code: corresp
    text: "Corresponding author. Email: vboyce@stanford.edu"
bibliography: ["251MA.bib"] # Replace with one or more of your own bibtex files. Better BibTeX for Zotero is your friend
csl: dmk-format.csl # Use any CSL style. See https://www.zotero.org/styles for a good list. Ignored if citation_package: natbib
link-citations: TRUE
output:
  bookdown::pdf_document2:
    toc: FALSE
    keep_tex: TRUE
    template: generic_article_template.tex
    #md_extensions: "-autolink_bare_uris"
    number_sections: TRUE
    citation_package: default # Can also be "natbib"
lang: en # Main document language in BCP47 format
geometry: "margin=25mm"
papersize: a4
#linestretch: 2 # for double spacing
endfloat: FALSE # Set to TRUE to turn on latex endfloat package to place figures and tables at end of document
# endfloatoption: # See endfloat documentation for more possibilities
#   - tablesfirst # Default
#   - nomarkers # Default
numberlines: FALSE
authblk: TRUE # FALSE = author affiliations in footnotes; TRUE = author affiliations in a block below author names
footnotehyper: FALSE # TRUE will give you enhanced table footnote capabilities. Set to FALSE to be able to use French blocks. Needed due to what appears to be a latex bug.
urlcolor: blue
linkcolor: blue
citecolor: blue
graphics: TRUE # Needed to be able to include images
tables: TRUE # Needed to be able to include tables
# fancyhdr:
#   first:
#     #headleft: "REPORT-NO-XXXX"
#     headright: "Kaplan et al. (2021)"
#     headrulewidth: 0pt
#     #footleft: A left foot
#     footrulewidth: 0pt
#   subsequent:
#     #headleft: "NEXT-PAGE-HEADER-LEFT"
#     headright: "Kaplan et al. (2021)"
#     headrulewidth: 1pt
#     footrulewidth: 0pt

@@

We are aware of three large-scale replication efforts replicating experimental results in the existing psychology literature. RP:P sampled roughly 100 studies from top psychology journals in 2008 [@openscienceconsortium2015]. They found an overall replication rate around 40%, which provided evidence to support growing concerns about the non-reliability of the literature. [idk, maybe worth framing that this was a big deal study when it came out]. TODO some discussion of how many papers have reanalysed this cutting the data different ways.

The ManyLabs series of studies have also done large-scale replications of effects from psychology. Due to their primary goal of investigating different forms of hetereogeneity, their sampling has been non-representive, focusing on short studies with only two conditions. Across Many labs 1-3 foo bar replicated [@klein2014; @klein2018; @ebersole2016]. Many labs 5 was a re-replication attempt on 10 of RP:P and rescued 2/10 [@ebersole2020]. TODO look up details

@camerer2018 replicated the 21 behaviors studies published in Nature and Science from 2010-2015 that did not require special populations or special equipment. They found a roughly 60% replication rate.

In addition to determining estimated overall replicaiton rates for fields and journals, there's also merit in knowing what features of experiments (and replication attempts) are predictive of replication success. Blah blah stakeholders and resources. There's some signal here, as people are able to predict replication success at above chance CITATIONS @hoogeveen2019. RP:P looked at how replication rates varied across subsamples of their studies. They found that cognitive psychology studies replicated at higher, but still low rates (50% v 25%) compared to social psychology. They also found that larger effect sizes and smaller p-values of original studies were predictive of replicating. TODO do we talk about any other correlates. There are reasons to believe that experimental factors such as number of items or between and within subject designs may also be predictive (cite our old paper), and could pontentially be some of the reason for subfield differences.

[could possibly frame with a bit of some=MCF have advocated teaching replication cite whatever, describe class, then thing? @frank2012; @hawkins]
Here we introduce a new dataset of replications in the behavioral sciences, primarily psychology. Over the years 2011-2022, students in a graduate-level experimental methods class have conducted online replications as individual course projects. From this, we have 176 experimental replications that were codeable. This approximately doubles the set of experiments in the large-scale replication literature. We investigate predictors of replicability in this new dataset.

@@

As secondary outcomes, we also calculated prediction intervals following @errington2021 on the key measure of interest from each study. Because of variable statistics and reporting, this was calculable on FOOBAR studies.

@@

Across the 176 studies, the overall replication rate was 49% TODO derive in code. FOOBAR % of the studies had replication outcomes within the prediction interval of the original outcome. The average p_original value (median?) was TODO.

For the FOOBAR studies with SMD, we see cite FIGURE.

@@

[ there is controversy here, but to even discuss it, we need empirics] Even those who argue that replication is not so essential still rely on data from replications to make their cases that replication rates are not as low as they seem and that these replication rates are acceptable. @lewandowsky2020

@@

This subjective replication outcome was chosen because it already existed, could be applied to all projects (regardless of type and detail of statistical reporting), and did not rely solely on one statistical measure. As a complement, we also identified a "key" statistical test for each paper (see below for details), and if possible, computed p_original and prediction interval at this statistic, following @errington2021. p_original was a continuous measure of the p-value on the hypothesis that the original and replication samples come from the same distribution. Prediction interval was a binary measure of whether the replication outcome fell within the prediction interval of the original outcome measure.
